Implementing Capon Beamforming on the GPU for Real Time Cardiac Ultrasound Imaging

### 2013-01-29 HRUIonGPU/jrnl_article.tex
uffc

\begin{abstract}
%\boldmath
...
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

@@

In the next section we present background information about the Capon beamformer and the GPU computing model. In Section \ref{sec:meth} we go in detail about the parallel implementation of the Capon beamformer, before in Section \ref{sec:bs} we introduce the beamspace method and how it has been implemented on the GPU. Benchmark results and resulting images are presented in Section \ref{sec:res}, and finally we discuss the results in Section \ref{sec:dis}, and draw conclusions in Section \ref{sec:con}.

@@

From (\ref{eq:R}) it is obvious that calculating one element of $\mat{\hat{R}}$ is independent of all other elements. A natural level of granularity would then be to assign one thread to each element of $\mat{\hat{R}}$ \cite{Chen2011}. This will minimize global reads and writes needed per thread, but unfortunately the maximum number of threads per block puts an upper limit on the subarray length, $L_{max}=32$, since we want to avoid block-to-block synchronization. Since arrays of 96-128 elements are common in medical ultrasound imaging an implementation not limited by $L_max=32$ is preferable.

@@

For the results presented in this paper, we have used a GPU implementation of batched Gauss-Jordan (GJ) elimination made by Nvidia to solve $\mat{\hat{R}}\vec{b} = \vec{1}_L$, where $\vec{b} = \mat{\hat{R}}^{-1}\vec{1}_L$ for all pixels at once. The solver has been made available for registered CUDA developers.%For smaller systems, $L < 10$, a direct solver using one thread per system is preferable. For this purpose we have implemented Cramer's rule for $2 \times 2$, $3 \times 3$ and $4 \times 4$ matrices. All solvers have been benchmarked against the latest Intel MKL libraries.

@@

The final output, as shown in (\ref{eq:z_mv}) and (\ref{eq:z_mv2}), can be formed by either reducing the data down to length $L$, or increase the weight vector to length $M$. Since the design is $L$ threads per output, the data is reduced to length $L$ by letting thread $r$ calculate 
\begin{align}\label{eq:subsum}
\breve{x}_{r} = \sum_{k=r}^{r+N_L-1}x_{k} \text{ for } r \in [0, L-1].
\end{align}
Each thread now computes $z_r = w_r^*x_r$, and finally one thread computes and outputs $z = \frac{1}{N_L}\sum_{r=0}^{L-1} z_r$ to global memory. %The last sum can also be performed using a binary reduction sum across several threads for increased speed.

@@

The beamspace version of the Capon beamformer is derived by replacing the covariance matrix in (\ref{eq:w}) with the beamspace covariance matrix 
\begin{align}
\mat{\hat{R}}_{BS} = f(\vec{x}_{BS}) = f(\mat{B}\vec{x}), 
\end{align}
where $\mat{B} \in \mathbb{C}^{N_b,L}$, and $N_b$ is the number of selected beams. The transformation must be performed per subarray, yielding subarrays that no longer overlap in space. Therefore, if the transformation is applied before the covariance matrix is constructed, the amount of input data is change from $M$ to $N_LN_b$ elements per sample, however all remaining steps will get lower complexity when $N_b < L$.

@@

Equation (\ref{eq:sliding_bs}) shows that instructions are saved if we utilize the overlap across subarrays, but with an increase in task parallel granularity (As discussed in Section \ref{sec:calcR}). The most obvious is to use one thread per beam (index $k$) that calculates this beam for all subarrays. However, since the number of selected beams usually is small ($N_b \ll M$) we will end up with a large memory per thread ratio. Using one thread per beam is therefore not feasible for small $N_b$ large $M$ configurations. The solution is to combine SBS with full computations. As shown in Fig. (???), a number of thread groups target different sets of subarrays which they transform using the SBS algorithm. In that way, the number of threads per sample is increased and thus the memory per thread ratio is decreased.

As mentioned the amount of channel data is increased from $M$ to $N_LN_b$ per sample in beamspace. This means that we no longer can exploit spatial overlap when calculating the sample covariance matrix, but since $N_b$ is small we can now allow to have one thread per element in $\mat{\hat{R}}_{BS}$. A kernel similar to the one described in \cite{Chen2011} has therefore been implemented. In addition, for small $N_b$ values, several covariance matrices are calculated per thread block to achieve high occupancy of the GPU.

After solving $\vec{b}_{BS} = \sqrt{L}\mat{\hat{R}}_{BS}^{-1}\vec{e}_1$, the beamspace weight vector is calculated as 
\begin{align}
\vec{w}_{BS} = \frac{\vec{b}_{BS}}{\sqrt{L}\vec{e}_1\vec{b}_{BS}} \in \mathbb{C}^{N_b}
\end{align}  
and applied to the beamspace data summed across subarrays,
\begin{align}
z[n] = \vec{w}_{BS}^H\sum_{l=0}^{L-1}\vec{x}_{BS,l}. 
\end{align}

@@

As presented in (\ref{eq:diag}), adaptive diagonal loading is performed by loading the sample covariance matrix with the average energy per element, hence $trace\{\mat{\hat{R}}\}/L$. When data are transformed into beamspace, a high percentage of the total energy is mapped to a small subset of beams. Thus the average energy per beam is higher than the average energy was per element, when beams containing little energy are removed. This means that less diagonal loading (smaller $d$) has to be applied in beamspace than in element space when $N_b < L$.

@@

\section{Benchmarks}\label{sec:res}

@@

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_bar_bs_M=64_Nx=80_Ny=400_Nb=3.png} \label{fig:benchBS3}}
\hfil
\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_bar_bs_M=96_Nx=120_Ny=400_Nb=3.png}%
\label{fig:benchBS5}}}
\caption{Benchmark of GPU beamspace Capon beamforming for a cardiac image covering a $70 \degree$ and $15$cm deep sector. Execution time is plotted as a function of subarray length $L$.  If $L$ is kept constant on $M/2$ and execution time is plotted against $N_b$, the plot would be similar to the two in Fig. \ref{fig:bench}. (a) 64 elements array. (b) 96 elements array.}
\label{fig:benchBS}
\end{figure*}
In this section we present benchmarks of the implementations presented in Section \ref{sec:meth} and \ref{sec:bs} performed on a Nvidia Quadro 6000 graphics card (14 SMs, 1 TFlops theoretical single precision, 6 GB global memory, and 144 GB/s memory bandwidth). Problem sizes are calculated based on 32, 64, and 96 element phased arrays with a 2.5 MHz center frequency. Assuming a system bandwidth of 80\% we need a complex sampling frequency of 2 MHz, and when imaging down to a depth of 15 cm we end up with approximately 400 samples per range line. To correctly sample a $70\degree$ sector with 32, 64 and 96 element arrays ($\lambda/2$ pitch), we need at least 40, 80 and 120 beams respectively. The presented execution times do not include transfer of data from CPU-side to the GPU, since data are assumed to be pre-delayed and available in GPU memory. What is included are all calculations, memory transfers from global to near-core GPU memory, and near core memory access.

@@

\section{Simulated phantom and \textit{in-vivo} cardiac images}

@@

\section{Trading resolution for speed}
As we see from Fig. \ref{fig:bench} and \ref{fig:benchBS}, execution time is reduced when either $L$ or $N_b$ is reduced. So to gain an  increase in processing throughput we can reduce $L$ or $N_b$. The question is how does this impact image quality. In Fig. \ref{fig:speed_res_trade} minimum distance between the two point targets in Fig. \ref{fig:phantom} (while preserving a 6dB lower level in between) is plotted against $L$ (when processed with Capon) and $N_b$ (when processed with BS Capon). For high values the two methods are equal, but for lower values, BS Capon provides higher resolution than what is possible with small subarrays. For this result, $d=0.01$ has been used on both methods. Why resolution decreases for BS Capon for small $N_b$s is partially explained by reduced information of interference at higher angles, and an automatically increase in diagonal loading. It is also interesting to see that Capon beamforming performs worse than DAS for small subarrays. (Comment on beamspace).

@@

\section{Discussion}\label{sec:dis}
In this paper we have presented a parallel implementation of the Capon beamformer both in element- and beam-space. The processing rates acquired shows that it is now possible to apply BS Capon in real time in cardiac ultrasound imaging. From Fig. ... 2MLA is supported.

From Fig. \ref{fig:benchUS64} we see that for $L = M/2 = 32$ and $K=1$, the total execution time is 100 ms (10 fps). Taking into account that we use complex data, but less samples per image, this is similar to the performance reported by Chen et al. \cite{Chen2011}. For the 32 element array in Fig. (\ref{fig:benchUS32}), execution time is reduced to 11.5 ms (87 fps) using the same settings ($L=M/2, K = 1$). Doubling this number can be interpreted as pre-beamforming a 64 element array down to 32. The frame rate for a 64 element array is then increased from 10 to 44 fps. Note that lateral oversampling will increase the total execution time with a factor equal the amount of oversampling.

A major part of the total execution time comes from solving systems of linear equations. This limitation is targeted by reducing the sample covariance matrix size in a novel way \cite{Nilsen2009}.

We have shown that the Capon beamformer can be implemented in a GPU framework. And if we as in \cite{Chen2011} define real-time as 10 fps, all execution times  in Fig. (\ref{fig:bench}) are real time. If we on the other hand define real-time as the time it takes to acquire a given image, the image formed using a 32 and 64 element array has a real time requirement of 125 fps and 62.5 fps respectively. There is some distance to cover before that goal is reached for all values of $L \le M/2$. However we see that real time, by the last definition, is possible for $M=64, L < 16$, and for $M = 32, L < 13$. Another option to reach real-time execution is to use several GPUs simultaneously. Note that multi-line acquisition will increase the frame rate requirement accordingly.

In the attached video of a simulated phantom one can see that Capon beamforming highly resolves moving point targets. The beamformer is shift invariant as long as the lateral sampling is increased. No major improvement in contrast is observed. In the cardiac recording, structures are thinner when the Capon beamformer is applied, however we observe a loss in contrast due to signal cancellation. Future work should focus on solving this issue.

We expect that a large speedup had the Capon beamformer been implemented on the CPU using threads and SIMD (single instruction multiple data) instructions.

Solving linear systems on the GPU is not believed to be much faster than a CPU implementation, but there is two key points. First the CPU is offloaded, and second the time it takes to transfer all covariance matrices back to the CPU makes the choice of doing the solving on the GPU simple to make.

(results)?
For a typical cardiac ultrasound image of 80*400 pixels (70 degree sector, 15cm range) acquired using a 2.5MHz, $M=64$ element phased array, the result is 10fps (subarray length $L=M/2$, temporal smoothing over 3 samples). If we do a 2-element pre-beamforming to get the channel count down to 32, the frame rate increases to 44fps. For a 32 element phased array we need less beams to cover the sector ($40 \times 400$ pixels), hence with the same parameters the frame rate increases to 87fps. The bottleneck of the Capon algorithm is to find the inverse covariance matrix for all pixels. This is an $O(L^3)$ operation, and results show that when L is larger than 16, real time performance is not possible for cardiac imaging with current high-end hardware. The target GPU has been Nvidia’s Quadro 6000, capable of 1Tflops.

How does beamspace perform when using plane wave imaging...?

MLA's has, to some extent be used to increase later sampling. When using a high resolution beamformer, Nyquist tells us that the sampling frequency must be increase. Future work will concentrate on how much over sampling is required when using the Capon beamformer whit i curtain set of parameters.

\section{Conclusion}\label{sec:con}
...

\section{Future work}
Plane waves...

>>>>

\begin{abstract}
%\boldmath
Capon beamforming for   
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

@@

In the next section we present background information about the Capon beamformer and the GPU computing model. In Section \ref{sec:meth} we go in detail about the parallel implementation of the Capon beamformer, before in Section \ref{sec:bs} we introduce the beamspace method and how it has been implemented on the GPU. Benchmark results and resulting images are presented in Section \ref{sec:bench} and \ref{sec:images}, together with a discussion of trading image quality for speed in Section \ref{sec:trade}.  Finally we discuss the results in Section \ref{sec:dis}, and draw conclusions in Section \ref{sec:con}.

@@

From (\ref{eq:R}) it is obvious that calculating one element of $\mat{\hat{R}}$ is independent of all other elements. A natural level of granularity would then be to assign one thread to each element of $\mat{\hat{R}}$ \cite{Chen2011}. This will minimize global reads and writes needed per thread, but unfortunately the maximum number of threads per block puts an upper limit on the subarray length, $L_{max}=32$, since we want to avoid block-to-block synchronization. Since arrays of 96-128 elements are common in medical ultrasound imaging an implementation not limited by $L_{max}=32$ is preferable.

@@

For the results presented in this paper, we have used a GPU implementation of batched Gauss-Jordan (GJ) elimination made by Nvidia to solve $\mat{\hat{R}}\vec{b} = \vec{1}_L$, where $\vec{b} = \mat{\hat{R}}^{-1}\vec{1}_L$, for all pixels at once. The solver has been made available online for registered CUDA developers.%For smaller systems, $L < 10$, a direct solver using one thread per system is preferable. For this purpose we have implemented Cramer's rule for $2 \times 2$, $3 \times 3$ and $4 \times 4$ matrices. All solvers have been benchmarked against the latest Intel MKL libraries.

@@

The final output, as shown in (\ref{eq:z_mv}) and (\ref{eq:z_mv2}), can be formed by either reducing the data down to length $L$, or increase the weight vector to length $M$. Since the design is using $L$ threads per output, the data is reduced to length $L$ by letting thread $r$ calculate 
\begin{align}\label{eq:subsum}
\breve{x}_{r} = \sum_{k=r}^{r+N_L-1}x_{k} \text{ for } r \in [0, L-1].
\end{align}
Each thread now computes $z_r = w_r^*x_r$, and finally one thread computes and outputs $z = \frac{1}{N_L}\sum_{r=0}^{L-1} z_r$ to global memory. %The last sum can also be performed using a binary reduction sum across several threads for increased speed.

@@

The beamspace version of the Capon beamformer is derived by replacing the covariance matrix in (\ref{eq:w}) with the beamspace covariance matrix 
\begin{align}
\mat{\hat{R}}_{BS} = f(\vec{x}_{BS}) = f(\mat{B}\vec{x}), 
\end{align}
where $\mat{B} \in \mathbb{C}^{N_b,L}$, and $N_b$ is the number of selected beams. If the transformation is applied before the covariance matrix is constructed, one transformation must be performed per subarray, yielding subarrays that no longer overlap in space. The amount of input data is then change from $M$ to $N_LN_b$ elements per sample, however all remaining steps will get lower complexity when $N_b < L$.

@@

Equation (\ref{eq:sliding_bs}) shows that instructions are spared if we utilize the overlap across subarrays, but with an increase in task parallel granularity (As discussed in Section \ref{sec:calcR}). The most obvious is to use one thread per beam (index $k$) that calculates this beam for all subarrays. However, since the number of selected beams usually is small ($N_b \ll M$) we will end up with a large memory per thread ratio. Using one thread per beam is therefore not feasible for small $N_b$ large $M$ configurations. The solution is to combine SBS with full computations. As shown in Fig. (???), a number of thread groups target different sets of subarrays which they transform using the SBS algorithm. In that way, the number of threads per sample is increased and thus the memory per thread ratio is decreased.

As mentioned, the amount of channel data is increased from $M$ to $N_LN_b$ per sample when using SBS. This means that the spatial overlap exploited when calculating the sample covariance matrix in element space is no longer available. On the other hand, since $N_b$ should be small ($N_b < 32$), one thread per element in $\mat{\hat{R}}_{BS}$ is now doable. A kernel similar to the one described in \cite{Chen2011} has therefore been implemented. In addition, for small $N_b$ values, several covariance matrices are calculated per thread block to achieve high occupancy of the GPU.

After solving $\vec{b}_{BS} = \sqrt{L}\mat{\hat{R}}_{BS}^{-1}\vec{e}_1$, the beamspace weight vector is calculated as 
\begin{align}
\vec{w}_{BS} = \frac{\vec{b}_{BS}}{\sqrt{L}\vec{e}_1\vec{b}_{BS}} \in \mathbb{C}^{N_b}
\end{align}  
using on thread per beam, and applied to the beamspace data summed across subarrays,
\begin{align}
z[n] = \vec{w}_{BS}^H\sum_{l=0}^{L-1}\vec{x}_{BS,l}. 
\end{align}
And again are several pixels calculated per thread block for small values of $N_b$ in order to achieve high GPU occupancy. The beamspace data summed across subarrays are calculated and outputted as part of the SBS kernel.

@@

As presented in (\ref{eq:diag}), adaptive diagonal loading is performed by loading the sample covariance matrix with the average energy per element, hence $trace\{\mat{\hat{R}}\}/L$. When data are transformed into beamspace, a high percentage of the total energy is mapped to a small subset of beams. Thus the average energy per beam is higher than the average energy was per element when beams containing little energy are removed. This means that less diagonal loading (smaller $d$) has to be applied in beamspace than in element space when $N_b < L$.

@@

\section{Benchmarks}\label{sec:bench}

@@

\begin{figure*}[!t]
\centerline{\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_bar_bs_M=64_Nx=80_Ny=400_Nb=3.png} \label{fig:benchBS64}}
\hfil
\subfloat[]{\includegraphics[width=3.5in]{gfx/benchmark_bar_bs_M=96_Nx=120_Ny=400_Nb=3.png}%
\label{fig:benchBS96}}}
\caption{Benchmark of GPU beamspace Capon beamforming for a cardiac image covering a $70 \degree$ and $15$cm deep sector. Execution time is plotted as a function of subarray length $L$.  If $L$ is kept constant on $M/2$ and execution time is plotted against $N_b$, the plot would be similar to the two in Fig. \ref{fig:bench}. (a) 64 elements array. (b) 96 elements array.}
\label{fig:benchBS}
\end{figure*}
In this section we present benchmarks of the implementations presented in Section \ref{sec:meth} and \ref{sec:bs} performed on a Nvidia Quadro 6000 graphics card (14 SMs, 1 TFlops theoretical single precision, 6 GB global memory, and 144 GB/s memory bandwidth). Problem sizes are calculated based on 32, 64, and 96 element phased arrays with a 2.5 MHz center frequency. Assuming a system bandwidth of 80\% we need a complex sampling frequency of 2 MHz, and when imaging down to a depth of 15 cm we end up with approximately 400 samples per range line. To correctly sample a $70\degree$ sector with 32, 64 and 96 element arrays ($\lambda/2$ pitch), we need at least 40, 80 and 120 beams respectively. The presented execution times do not include transfer of data from CPU-side to the GPU, since data are assumed to be pre-delayed and available in GPU memory. What is included are all calculations, memory transfers from global to near-core GPU memory, and near core memory access.

@@

\section{Simulated phantom and \textit{in-vivo} cardiac images}\label{sec:images}

@@

\section{Trading resolution for speed}\label{sec:trade}
As we see from Fig. \ref{fig:bench} and \ref{fig:benchBS}, execution time is reduced when either $L$ or $N_b$ is reduced. So to gain an  increase in processing throughput we can reduce $L$ or $N_b$. The question is how does this impact image quality. In Fig. \ref{fig:speed_res_trade} minimum distance between the two point targets in Fig. \ref{fig:phantom} (while preserving a 6dB lower level in between) is plotted against $L$ (when processed with Capon) and $N_b$ (when processed with BS Capon). For high values the two methods are equal, but for lower values, BS Capon provides higher resolution than what is possible with small subarrays. For this result, $d=0.01$ has been used on both methods. Why resolution decreases for BS Capon for small $N_b$s is partially explained by reduced information of interference at higher angles, and an automatically increase in diagonal loading. It is also interesting to note that Capon beamforming in this example performs worse than DAS for small subarrays.

@@

\section{Discussion}\label{sec:dis}
In this paper we have presented a parallel implementation of the Capon beamformer in both element- and beam-space for high resolution cardiac ultrasound imaging. The results show that it is now possible to apply BS Capon in real time in cardiac ultrasound imaging utilizing the power of GPU's. According to Fig. \ref{fig:benchBS} two parallel receive lines is also within reach (for both $M=64$ and $M=96$.  $L=M/2$), but at the moment it is unknown if these extra lines is needed for increased sampling or not. Another concern is that lateral oversampling using parallel receive lines will increase the total execution time with a factor equal the amount of oversampling.

For Capon in element space, processing rates for high quality settings is still to high to support real time cardiac ultrasound imaging. From Fig. \ref{fig:benchUS64} we see that for $L = M/2 = 32$ and $K=1$, the total execution time is 100 ms (10 fps). Taking into account that we use complex data, but less samples per image, these results are similar to the performance reported by Chen et al. \cite{Chen2011}. For the 32 element array in Fig. (\ref{fig:benchUS32}) execution time is reduced to 11.5 ms (87 fps) using the same settings ($L=M/2, K = 1$).

A major part of the total execution time for element space Capon comes from solving the system of linear equations. This limitation is targeted by reducing the sample covariance matrix size in beamspace. As shown in Fig. \ref{fig:benchBS}, inverting the three times three beamspace covariance matrix is barely visible. The time taken to construct all covariance matrices is also reduced, but for few beams this is now the major contributor to the total time. If real time is defined as 10 fps \cite{Chen2011} all execution times in both Fig. \ref{fig:bench} and \ref{fig:benchBS} are real time. More natural for cardiac ultrasound imaging is to define real-time as the time it takes to acquire the underlying image. With this requirement the images formed using a 32, 64 and 96 element array has a real time requirement of 125, 62.5 and 41.7 fps respectively using single line acquisition. Each benchmark plot has a line indicating this real time requirement. With beamspace, all processing times for large subarrays are below this line.

This paper further shows how to obtain a parallel Capon beamformer, and how it can be implemented in a GPU framework. The per-pixel granularity suggest that the beamformer is easily dividable across multiple GPUs. Another option to reach real-time execution for all cases presented in this paper is therefore to use several GPUs simultaneously. In that case, processing rates are increased with a factor equal to the number GPUs. However, there is usually a space-cost-energy limitation for how many GPUs that can be fitted in an ultrasound scanner.

Turning to image quality we see from Fig. \ref{fig:phantom}, and the attached video of the simulation, that Capon beamforming highly resolves moving point targets both in element- and in a reduced beam-space. Our preliminary finding is that the Capon beamformer is shift invariant as long as the lateral sampling is increased enough. No major improvement in contrast is visually observed in these images. In the cardiac recording (Fig. \ref{fig:invivo}), structures are thinner and better resolved both when the Capon and BS Capon beamformer is applied. However we observe a loss in contrast, especially in the septum (Fig. \ref{fig:slices}). This loss can be partially explained by the present of highly correlated signals and errors in the assumed steering vector. Future work should focus on solving this issue.

Nilsen et. al suggest to do automatic selection of beams in beamspace, hence picking the beams containing most energy. In this paper the center beams are always picked. This seems to work fine, but an adaptive pick of beams should be implemented if interference at high angles is shown to contaminate the image.

%We expect that a large speedup had the Capon beamformer been implemented on the CPU using threads and SIMD (single instruction multiple data) instructions.

%For a typical cardiac ultrasound image of 80*400 pixels (70 degree sector, 15cm range) acquired using a 2.5MHz, $M=64$ element phased array, the result is 10fps (subarray length $L=M/2$, temporal smoothing over 3 samples). If we do a 2-element pre-beamforming to get the channel count down to 32, the frame rate increases to 44fps. For a 32 element phased array we need less beams to cover the sector ($40 \times 400$ pixels), hence with the same parameters the frame rate increases to 87fps. The bottleneck of the Capon algorithm is to find the inverse covariance matrix for all pixels. This is an $O(L^3)$ operation, and results show that when L is larger than 16, real time performance is not possible for cardiac imaging with current high-end hardware. The target GPU has been Nvidia’s Quadro 6000, capable of 1Tflops.

\section{Conclusion}\label{sec:con}
In this paper we have shown that the Capon beamformer can be accelerated using GPUs. For beamspace Capon beamforming processing rates supporting real time cardiac ultrasound imaging is shown to be possible. Image quality is investigated both in a simulated phantom and in \textit{in-vivo} cardiac data. Results shows that Capon beamforming is feasible for cardiac ultrasound imaging, providing images with highly resolved structures.

\section{Future work}
Study shift invariance and minimum sampling...

MLA's has, to some extent been used to increase later sampling. When using a high resolution beamformer, Nyquist tells us that the sampling frequency must be increase. Future work will concentrate on how much over sampling is required when using the Capon beamformer whit i curtain set of parameters...

Plane waves...
